A Comparative Quality Metric for Fuzzing with Logic State Coverage

### 2024-03-03 paper/main.tex
paper: de-bucketed

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/repr.pdf}
  \caption{Example control flow graph and the number of program behaviors
  (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
  of the branch $b$. Dotted lines demarcate the start of a new power-of-2 branch
  hit count.}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:repr}
\end{figure}

@@

Logic states distinguish the program behaviors with smaller branch hit counts
in finer details (i.e., distinguishing \emph{interesting} behaviors) but
coalesce the behaviors with larger hit counts (i.e., avoiding
over-representation of \emph{uninteresting} behaviors). This results in a larger
number of covered logic states (i.e., larger logic state coverage) when the
observed program behaviors are more interesting.

@@

\autoref{f:repr} shows an example control-flow graph and the number of possible
program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
count of the branch $b$. For example, there are 
two possible program behaviors, $b_2$ after $b_1$ or $b_1$ after
$b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
%Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
%
The dotted lines demarcate the beginning of a new power-of-2 branch hit count
(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
bucket. Each region surrounded by dotted lines constitutes \emph{one logic
state}, as all contained program behaviors fall into the same integer bucket
in every branch.

%Notice that a program behavior is deemed more interesting as it exhibits
%smaller branch hit counts (\autoref{s:fuzz:unfuzz}). 
As shown, a logic state distinguishes more interesting program behaviors in a
finer granularity, representing fewer behaviors with smaller branch hit counts
(i.e., bottom left). On the other hand, it coalesces more behaviors when
the branch hit counts get larger, where individual behaviors are deemed less
interesting. 
%
This results in a larger number of covered logic states when the observed
behaviors are more interesting (e.g., three program behaviors result in
three different logic states when $m(b_3)<2$) while the opposite happens when
they are not (e.g., a total of 11,950 behaviors fall into \emph{one} logic state
when $4 \le m(b_1) < 8$ and $4 \le m(b_2) < 8$).

%\autoref{f:repr} reveals two important properties of logic states. First, a
%logic state distinguishes interesting program behaviors with smaller branch hit
%counts in a finer granularity. For example, a logic state represents
%exponentially fewer program behaviors as $m(b_1)$ and $m(b_2)$ approach to 1.
%Second, a logic state coalesces less interesting program behaviors that require
%high branch hit counts or exhibit specific branch ordering, avoiding
%over-representation of them. For example, all 11,950 program behaviors
%exhibiting different branch ordering with $4 \le m(A) \le 7$ and $4 \le m(B) \le
%7$ are lumped into \emph{one} logic state.

@@

\autoref{f:design} illustrates the workflow of logic state coverage
measurement. Similar to edge coverage, it first records and buckets the branch
hit counts of every execution, yielding a \emph{logic state} as a result 
(\autoref{s:design:rec}). Then, it adds the recorded logic state to a 
\emph{bloom filter} that represents a set of observed logic states, by setting
the hash indices (\autoref{s:design:up}).  Finally, the measurement periodically
reads off the bloom filter to count the number of observed logic states
(\autoref{s:design:count}).

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/repr.pdf}
  \caption{Example control flow graph and the number of program behaviors
  (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
  of the branch $b$. Dotted lines demarcate whether the corresponding branch is
  hit or not (i.e., presence in a logic state).}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:repr}
\end{figure}

@@

Logic states distinguish the program behaviors with less branch repetitions in a
finer granularity, resulting in a higher number of covered logic states (i.e.,
larger coverage) as the observed program behaviors are more interesting.

@@

\autoref{f:repr} shows an example control-flow graph and the number of possible
program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
count of the branch $b$. For example, there are two possible program behaviors,
$b_2$ after $b_1$ or $b_1$ after $b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
%Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
%
The dotted lines demarcate whether the corresponding branch is hit or not, which
also corresponds to the presence of the branch in a logic state.
%the beginning of a new power-of-2 branch hit count
%(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
%bucket. 
The surrounded region has the same set of satisfied branches, constituting
\emph{one logic state}.

As shown, the program behaviors with more repetitive branches are grouped with
more program behaviors as one logic state.  For example, a program behavior
having only one repetitive branch (either $b_1$ or $b_2$) falls into the slim
logic states adjacent to axis (bottom right and top left), while a behavior
having two repetitive branches (both $b_1$ and $b_2$) falls into the large logic
state (top right). This results in observing repetitive (i.e., less interesting)
program states represented by fewer logic states, leading to smaller logic state
coverage.

%%Notice that a program behavior is deemed more interesting as it exhibits
%%smaller branch hit counts (\autoref{s:fuzz:unfuzz}). 
%As shown, a logic state distinguishes more interesting program behaviors in a
%finer granularity, representing fewer behaviors with smaller branch hit counts
%(i.e., bottom left). On the other hand, it coalesces more behaviors when
%the branch hit counts get larger, where individual behaviors are deemed less
%interesting. 
%%
%This results in a larger number of covered logic states when the observed
%behaviors are more interesting (e.g., three program behaviors result in
%three different logic states when $m(b_3)<2$) while the opposite happens when
%they are not (e.g., a total of 11,950 behaviors fall into \emph{one} logic state
%when $4 \le m(b_1) < 8$ and $4 \le m(b_2) < 8$).

@@

\autoref{f:design} illustrates the workflow of logic state coverage
measurement. Similar to edge coverage, it first records the \emph{logic state}
of each execution via instrumentation (\autoref{s:design:rec}). Then, it adds
the recorded logic state to a \emph{bloom filter} that represents a set of
observed logic states, by setting the hash indices (\autoref{s:design:up}).
Finally, the measurement periodically reads off the bloom filter to count the
number of observed logic states (\autoref{s:design:count}).
